---
title: Assignment 10
author: Katy Linich
date: 21 April 2020
output: html_notebook
---

#1-------------------------------------------------------------------------------------------------
```{r}
library(tidyverse)
```
```{r}
ELA_data <- read_csv("Johnson Elementary ELA Project.csv", skip = 3)
ELA_data <- fill(ELA_data, X1, .direction = c("down"))
ELA_data <- drop_na(ELA_data)
ELA_data <- rename(ELA_data, Room=X1)
ELA_data
                     
new_ELA_data <- ELA_data %>%
                  separate(`Tardies; Absences`, into = c('Tardies', 'Absences'), convert = TRUE)

new_ELA_data
```

#2-------------------------------------------------------------------------------------------------

```{r}
ELA_by_room <- new_ELA_data %>%
  group_by(Room)

ELA_by_room %>%
  summarise('Avg Tardies'=mean(Tardies), 'Avg Absences'=mean(Absences))
  
```

#3-------------------------------------------------------------------------------------------------
Write a script to show the frequency of missing data points for each quarter by room

```{r}
ELA_missing <- ELA_data %>%
  group_by(Room)%>%
  summarise("1st Q Missing" = sum(is.na(`1st Quarter`)), "2nd Q Missing"=sum(is.na(`2nd Quarter`)), "3rd Q Missing"=sum(is.na(`3rd Quarter`)),"4th Q Missing"=sum(is.na(`4th Quarter`)))
ELA_missing
```

#4-------------------------------------------------------------------------------------------------

**This does not show the trend very well. (-5)**

```{r}
ELA_data_quarters <- ELA_data %>%
   gather('1st Quarter', '2nd Quarter', '3rd Quarter', '4th Quarter', 
          key = "Quarter", value = "Rating") %>%
  group_by(Room, Quarter) %>%
  summarise(medians=median(Rating))
ELA_data_quarters

ggplot(ELA_data_quarters, aes(Quarter, medians, color=Room)) + geom_point()

```

#5-------------------------------------------------------------------------------------------------
Use the NYC flights data to construct a graph that compares carriers in terms of theproportion of 2013 flights that arrived on time when traveling from New York City toAtlanta. Your graph should include a title and easy-to-read labels, including the namesof airlines rather than airline codes. 

**This is labeled as "proportions" (which it should be), but you are showing frequencies. (-5)**

```{r}
flights <- read_csv("NYC FLights 2013.csv")

flights_by_dest <- flights %>%
  filter(dest=="ATL") %>%
  mutate(prompt=(arr_delay==0))
flights_by_dest

ggplot(flights_by_dest, aes(x=carrier)) + geom_bar(aes(fill=prompt)) + scale_x_discrete(labels= c("9E"="Endeavor Air","DL"="Delta", "EV"="ExpressJet", "FL"="AirTran", "MQ"="Envoy Air", "UA"="United Airlines", "WN"="Southwest"), name= c("Airline")) + labs(title= "Proportion of On Time Flights From NYC to Atlanta in 2013") + scale_fill_discrete(labels=c("Late", "On Time"))
  
```


